---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300,
  type = 'cairo'
)
```

# sift

<!-- badges: start -->
<!-- badges: end -->

sift facilitates **intelligent** & **efficient** exploration of datasets.

* `klassify` - reveals **implicit grouping** in continuous data.

* `kollate`

* `sift` - **augmented** dataset subsetting.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("sccmckenzie/sift")
```

### `klassify`

Imagine 1D K-means, except K is chosen automatically. As an example, consider the `faithful` dataset. 

```{r}
head(faithful$eruptions)
```

The density plot below clearly demonstrates there are **2** clusters of eruptions.

```{r echo = FALSE, fig.height=2}
library(ggplot2)

ggplot(faithful, aes(eruptions)) +
  geom_density() +
  geom_rug() +
  theme_minimal()
```

Currently, these clusters are *implicit*, meaning we do not have a categorical variable associating each observation with a cluster. We could assign observations less than, say, 3.0 to Group 1 and the remainder to Group 2.

`klassify` does this automatically - no extra inputs needed.

```{r}
library(sift)

k <- klassify(faithful$eruptions)

head(k)
```


```{r echo = FALSE, fig.height=2}
faithful$k <- k

ggplot(faithful, aes(eruptions)) +
  geom_density() +
  geom_rug(aes(color = factor(k))) +
  theme_minimal() +
  scale_color_discrete(name = "k")
```


### `sift`

Imagine `dplyr::filter()` that includes neighboring observations.
