---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300,
  type = 'cairo'
)
```

# sift

<!-- badges: start -->
<!-- badges: end -->

sift facilitates **intelligent** & **efficient** exploration of datasets.

``` r
# install.packages("devtools")
devtools::install_github("sccmckenzie/sift")
```

### `kluster`

Imagine 1D K-means, except K is chosen automatically. As an example, consider the `faithful` dataset. 

The density plot below clearly demonstrates there are **2** clusters of eruptions.

```{r echo = FALSE, fig.height=2}
library(ggplot2)

ggplot(faithful, aes(eruptions)) +
  geom_density() +
  geom_rug() +
  theme_minimal()
```

Currently, these clusters are *implicit*, meaning we do not have a categorical variable associating each observation with a cluster. We could manually assign clusters by drawing a line at, say, 3.0.

`kluster` does this automatically - no extra inputs needed.

```{r}
library(sift)

k <- kluster(faithful$eruptions)
```


```{r echo = FALSE, fig.height=2}
faithful$k <- k

ggplot(faithful, aes(eruptions)) +
  geom_density() +
  geom_rug(aes(color = factor(k))) +
  theme_minimal() +
  scale_color_discrete(name = "k")
```

### `sift`

Imagine `dplyr::filter()` that includes neighboring observations.
